---
title: 'eControl Met +: Study about the results of the addition of a sulfonylurea, DPP4 inhibitors or SGLT2 inhibitors as a second antidiabetic drug in patients with diabetes mellitus type 2 in treatment with metformin and insufficient glycemic control'
author: "Jordi Real"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    df_print: paged
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


rm(list=ls())
memory.size(max=160000)

output_Rdata<-here::here("resultats","Output_metplus.RData")


# Càrrega de libreries 
library(compareGroups)


# Carrega d'objectes

load(output_Rdata)


```

## Study Objectives and Endpoints:

# The primary objective:

To compare the proportion of patients achieving the reduction in HbA1c values of at least 0.5%, a weight reduction of at least 3%, after the addition of a SU, an DPP-4i or an SGLT-2i to the treatment with metformin in patients with T2DM and insufficient glycemic control in the medium-long term, up to a maximum of 24 months of follow-up. 

***

# Secondary objectives: 

- To estimate the mean reduction of HbA1c and body weight separately after the addition of an SU, a DPP-4i or an SGLT-2i in patients with DM2 treated with metformin and insufficient glycemic control (up to 24 months).
- To assess the average reduction in systolic blood pressure after the addition of an SU, a DPP-4i or an SGLT-2i in patients with DM2 treated with metformin and insufficient glycemic control.
- To assess the evolution of lipid profile (mean total cholesterol, HDL, LDL, and triglycerides) after the addition of an SU, a DPP-4i or an SGLT-2i in patients with DM2 treated with metformin and insufficient control glycemic. 
- To assess  the adherence to treatment after the addition of an SU, a DPP-4i or an SGLT-2i in patients with DM2 treated with metformin and insufficient glycemic control.
- To assess  the percentage of suspensions/dropouts of treatment at 6, 12 and 24 months (persistence of treatment).
- To describe the relevant adverse reactions produced after the addition of an SU, an DPP-4i or an SGLT-2i in patients with DM2 treated with metformin and insufficient glycemic control.
- To describe the comorbidity profile and baseline clinical characteristics of patients with DM2 and insufficient control with metformin in monotherapy after addition of a treatment with SU, DPP-4i or SGLT-2i.
- the reductions will be evaluated up to 12 months and a maximum of 24 months after the addition of the treatment or end of follow-up.

***

# Flow chart    

```{r, message=FALSE, warning=FALSE, include=T, echo=FALSE,size="huge"}


flow_global

flow_global2


```

# Pre-post descriptive analysis 

```{r, message=FALSE, warning=FALSE, include=T, echo=FALSE,size="huge"}

export2md(taula1, caption = "Table 1: Sociodemographic variables pre matching (N=65312)")

export2md(taulaPS, caption = "Table 1: Sociodemographic variables post matching (N=5897)")



```

# Descriptive analysis

```{r, message=FALSE, warning=FALSE, include=T, echo=FALSE,size="huge"}



export2md(taules[[1]], caption = "Table 1: Sociodemographic variables")

export2md(taules[[2]], caption = "Table 2: Baseline comorbidity variables")

export2md(taules[[3]], caption = "Clinical variables related to T2DM")

export2md(taula_events, caption = "Table 5: Variables related to safety")


```

# Primary objective

To compare the proportion of patients achieving the reduction in HbA1c values of at least 0.5%, a weight reduction of at least 3%, after the addition of a SU, an DPP-4i or an SGLT-2i to the treatment with metformin in patients with T2DM and insufficient glycemic control in the medium-long term, up to a maximum of 24 months of follow-up. 

# Secondary objectives
To estimate the mean reduction of HbA1c and body weight separately after the addition of an SU, a DPP-4i or an SGLT-2i in patients with DM2 treated with metformin and insufficient glycemic control (up to 24 months).


```{r, message=FALSE, warning=FALSE, include=T, echo=FALSE,size="huge"}

export2md(taules[[4]], caption = "Variables related to treatment efficacy")


```





